\subsubsection*{Agenda}
\begin{enumerate}
	\item Platform decision - SVG or Swing
	\item Versioning
	\item IDE?
	\item Set up verisoning
	\item Report-writing
	\item How to get started
\end{enumerate}
\underline{1. Platform decision} \\
Will have decided using Java Swing. \\ \\
\underline{2. Versioning} \\
We will use git, since some group members are familiar with it. \\ \\
\underline{3. IDE?} \\
Eclipse is our decision. \\ \\
\underline{4. Set up versioning} \\
This is mostly done (it is done on most of our computers. The repository is working). \\ \\
\underline{5. Report writing} \\
We will write the repot in LaTeX.

\subsubsection*{Reflection}
\underline{Discussion of the main class structure (packages):}
\begin{itemize}
	\item Controller \\
		\textsl{Controller (main class)}
	\item View \\
		\textsl{MapPanel} \\
		\textsl{MainFrame} \\
		\textsl{View} \\
		\textsl{ViewListener}
	\item Model \\
		\textsl{Edge} \\
		\textsl{DataFilter} \\
		\textsl{KrakToXMLConverter} \\
		\textsl{Model} \\
		\textsl{XMLReader}
\end{itemize}
\underline{Other} \\
Our krak-data to XML converter from a previous assignment has been remade to include a "type" element

The XMLReader works on small XML files

At all points there is a general agreement.
We have decided to start by making a simple visualization, then improving the functionality step by step, making sure the basic implementations work as they should.

\subsubsection*{Work sheets}
\begin{itemize}
	\item The XMLReader is currently exceeding heap space \hfill \\
		\textsl{Niels will try to fix this}
	\item Read about k-d trees \hfill \\
		\textsl{Think about the possibility of using it as our main data structure}
\end{itemize}

\subsubsection*{Next meeting}
Wednesday, 19/3-2012, 18:30