Searching for locations and trips happens in the left side of the application.

To find a specific address on the map, all you need to do is to enter the address in the upper text field named "Point / from", and then press "Find". The address you have searched for will now be marked on the map with a little dot, and you will automatically be zoomed in to this point.

When you want to find a route from one point to another, you simply type in the address that you want to go from, in the "Point / from" field, and the address you want to go to in the "To" field. When you have entered the two desired addresses you press the "Find" button and the route will be drawn on the map with a pink color. 
It is also possible to swap the to address field, so that the "Point / from" address now becomes the "To" address and vice versa, by pressing the "Swap" button.

When entering an address into any of the text fields, there are some limitations to what you can search for. It is possible to search for any road name you want. While you are typing, a list of possible addresses that match what you have typed in, pops up, if such addresses can be found. It is possible to search for:
\begin{itemize}
	\item City only
	\item Zip code only
	\item City and zip code
	\item Street name with zip code and/or city
\end{itemize}
If you for example want to search for "\AA boulevarden" in Copenhagen, you will have to separate the city name and street name with a comma like "\AA boulevarden, K\o benhavn" and not "\AA boulevarden K\o benhavn". You will not be able to search for road numbers but only road names, so please have in mind that if a road is long, the map may not lead you to the exact location that you are searching for, but only to the road that you are searching for.

Below the "Swap" and "Find" buttons, two round buttons are located labelled "Fast" and "Short".

If the "Fast" button is chosen, which it is by default, the fastest route between the two addresses will be found. If the "Short" button is chosen, the shortest route will be found.

Below the two round buttons there are two values shown. "Distance" and "Time". "Distance" shows the distance from the starting address to the ending address in kilometres. "Time" shows the estimated time that the trip will take.

When searching for the fastest trip, the time displayed is the time the trip takesif you always drive to the legal speed limit. This makes it useful for cars, motorcycles, and other vehicles which can move at the speed limits.

When searching for the shortest trip, the time displayed is the time the trip takes if you constantly move at 5 km/h, which is about the average speed you move on foot.

The trips do not take into account neither one-way streets, nor streets that it is only allowed to use under certain circumstances, for example the fact that it is not legal to walk on highways.