
                Currently, the application has been tested on laptops running Mac OS X and Arch Linux, and some differences concerning the application exist.

                When resizing the window on Mac OS X, no message is sent to the application until the user stops resizing (releases the mouse button). On Arch Linux, each time the window is resized the slightest, a message is sent. We have therefore decided not to keep a constant width-height ratio, since this does not work correctly on a computer running Arch Linux, though this would be our preferred design choice. Instead, only the content of the frame is changed, in accordance to the resizing being done.

                When zooming on Mac OS X, a message with a number is sent, representing an amount to be zoomed. On Arch Linux however, the size of the number is always 1, making the zooming a very slow process.

                We are also experiencing some performance issues on on the Arch Linux platform. Especially on one of the laptops running Arch Linux, where testing of the program is very slow. This laptop is an older model with older hardware than the other three laptops. It uses more than a minute to start up (compared to around thirty seconds on the Macs), and it has problems drawing the route when searching for directions. While zooming and dragging it is very slow and one will quickly get tired of using the application on this laptop due to its bad performance.
                
                The second laptop running Arch Linux is also experiencing some minor problems. These problems mainly occur while entering an address to search for. While typing the address, the cursor freezes for around half a second before you see what you actually wrote. This is not a huge issue, but it still makes the program annoying to use and gives a bad user experience. This second Arch Linux laptop's hardware is almost similar to the hardware in the two Macs running Mac OS X, which have also been used for testing the program. But even though the hardware is almost alike, the Arch Linux laptop still performs significantly worse than the Macs. Due to this, we suspect the different platforms to have quite a big impact on how well the program runs, which, according to the "Java performance" site on Wikipedia, might very well be the case. 
