The application works as we want it to, and it passes the minimum requirements. It starts up a bit slow, but when it is up and running it runs fast and smooth, atleast on Mac OS X. There are additional features that we would have liked to implement, but did not implement due to the lack of time.

It is of our best conviction that the program is practical to use, though we do see possible improvements, and that the user finds it intuitive and quick to find the places and routes they want, even though we do not have any usability tests confirming this theory.

The thing that we are the least satisfied about, is the relatively long period of time, the application needs to start up. The start-up time is a problem area, where we would use some time to make improvements, were we to work on future versions of the program.

Another downside to the application is it's platform dependency. Though written entirely in \texttt{Java}, the program reacts very differently to user input on computers running Mac OS X and Arch Linux respectively. But doing to the application only being used by us under controlled environments, this is not the issue it would be, were the application to be distributed.

If we were to continue working on the application, we would spend more time adding additional features of the sole purpose that we believe that we would learn a lot from doing so. We find no reason in adding additional features, unless they "give something back". And we are quite satisfied with the amount of learning we have received during the making of this project.

Technical issues have at some points been time consuming, but at no point have they been too critical for us to overcome them without too much difficulty.

The process of making the project has been an overall pleasant experience with no real discussions or issues not concerning the project itself. We have maintained a structuring of our group meanings that have worked for us, and even though we at some points have not discussed the work to be done sufficiently, cause different modules to need refactoring in order to fit together, the issues have been rare and minor.

The product itself, and our satisfaction with it, reflects the positive and stable process that we feel, our group work has been.
