The testing of the applications consists of several different kinds of tests:
\begin{itemize}
	\item Blackbox tests of simple "$in \rightarrow out$" methods.
	\item Whitebox test for the method in which code execution according to different conditions could be an issue.
	\item Tests of data structures by building small instances of the data structures and invoking their methods, comparing the output to the expected output.
	\item General tests of the user interface performed by simply using the application, trying to make it perform in a matter not expected.
\end{itemize}
With each blackbox tests, whitebox tests, and test of a data structure, an expectancy table including the results are to be found in the appendix \ref{sec:Testing appendix} on page \pageref{sec:Testing appendix}. In addition to that, graphical representations for some of the tests of data structures are also included in the appendix.

The general tests of the user interface are not documented anywhere. But they have been essential in the making of the rest of the tests, since they have always been the basis of what to test.

Many of the tests have caused us to find issues concerning the application that until the execution of the tests were unknown, which we have then had the chance to either improve or in the worst case be aware of.

Our tests do not include usability tests other than the experience we have from using the application ourselves. But it is very limited how useful this experience is, since we, as we have also made the application, are not good representatives for the typical user. Though, when testing a part of the application made by another group member, the insights have at some points caused realizations of either issues or positive things about the user interface. We would very much have preferred to have at least one "real" usability test. But due to time issues, this was not possible. We do, however, have a general idea of the usability of the application, since the main structure of the user interface is quite close to that of the leading applications on the market. But we are quite certain that a usability test could reveal things we have not noticed about the application, them being good or bad.